MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-07-30 main/MSstatsPTM_Main.tex
Small

Additionally, when comparing the fold change estimation across all modified peptides, the proposed method showed a tighter distribution of estimated fold changes around the true fold change. Specifically, the inner quartile range (IQR) of the estimated fold change for the proposed method was on average 32.5\% smaller than Limma and ANOVA's IQR. While the mean of the estimated fold changes was generally correct for all methods, the proposed approach correctly estimated the fold change more often across all PTMs. This fold change comparison can be seen in {\bf Supplementary Figure~\ref{supp-fig:fc_boxplot}}.

>>>>

{\bf Supplementary Figure~\ref{supp-fig:fc_boxplot}} further compares the fold change estimation across all modified peptides. $MSstatsPTM$ showed a tighter distribution of estimated fold changes around the true fold change. Specifically, the inter-quartile range (IQR) of the estimated fold change for the proposed method was on average 32.5\% smaller than Limma and ANOVA's IQR. While the mean of the estimated fold changes was generally correct for all methods, the proposed approach correctly estimated the fold change more often across all PTMs.
